Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-11-22 latex/paper.tex
强调4层结构的各向异性最大

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 12:00:25
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

While the anisotropy lifetime in two layer structures affects more than that of group velocity, group velocity contributes most of anisotropy in multilayer structures with layers more than three.  FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures. The group velocity  along the two directions of  2 layers silicene ( include silicene) are basicly the same except for the frequency range of 12THz - 15THz in 2l1 structure whose  group velocities are highly anisotropic. Group velocity for the others exhibits similar curve and are all highly anisotropic both in low and high frequency range. The group velocity of zigzag direction are all large than that of zigzag. These results  show that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects in two layer silicene but the reverse for the structures thicker.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 14:17:59
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

While the anisotropy lifetime in two layer structures affects more than that of group velocity, group velocity contributes most of anisotropy in multilayer structures with layers more than three.  FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures. The group velocity  along the two directions of  bilayer silicenes are basicly the same except for the frequency range of 12THz - 15THz in 2l1 structure whose  group velocities are highly anisotropic. Group velocity for the others exhibits similar curves and are all highly anisotropic both in low and high frequency range. The group velocity of zigzag direction are all larger than that of zigzag.These results  show that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects in bilayer silicene but it's mainly from group velocity difference of the two directions in 3-6 layer silicenes. There's not much anisotropy in phonon lifetime in 3,5,6 layer structures but the structure with 4 layers has its anisotropy from both phonon lifetime and group velocity which lead to a largest anisotropy up to 69.98\%
